Profitability Prediction of Consulting Projects in the Construction Industry

### 2016-08-24 finalwriteup/draft.rmd
Appendix
started paper and checked appendix

* total amount invoiced * percent of job by professional level employee
* total amount invoiced * client id
* project category * number of employees on the job

@@

The second method was developed to overcome the problem of missing data. When all variables were combined, only 15% of the project cases had complete data and therefore the ANOVA test would eliminate 85% of the data upon execution. Imputing the missing data was not desirable at that stage due to the volume of missing categorical data and an inability to ensure the imputed data did not adversely influence results. The second method was a complicated procedure that required dozens of models but allowed variables with missing data to be included. First, a project was randomly selected (a row in the data set) which would have certain variables complete. The data was then filtered for all projects that had at least the same columns complete, and an ANOVA model was built on this reduced data set. This method allowed variables with a larger proportion of missing data to be included while not attempting to analyse all variables at once.

@@

The results of the ANOVA models were assessed using the RMSE statistic of the 'return per dollar' predictions. These were compared against a baseline RMSE, which was the RMSE of the predicted 'return per dollar' values less the mean 'return per dollar' of all projects.

>>>>

* total amount invoiced * percent of job by professional level employee
* project category * number of employees on the job

@@

The second method was developed to overcome the problem of missing data. When all variables were combined, only 15% of the project cases had complete data and therefore the ANOVA test would eliminate 85% of the data upon execution. Imputing the missing data was undesirable at that stage due to the volume of missing categorical data and an inability to ensure the imputed data did not adversely influence results. The second method was a complicated procedure that required dozens of models but allowed variables with missing data to be included. First, a project was randomly selected (a row in the data set) which would have certain variables complete. The data was then filtered for all projects that had at least the same columns complete, and an ANOVA model was built on this reduced data set. This method allowed variables with a larger proportion of missing data to be included while not attempting to analyse all variables at once.

@@

The results of the ANOVA models were assessed using the RMSE statistic of the 'return per dollar' predictions. These were compared against a baseline RMSE, which was the RMSE of the predicted 'return per dollar' values less the mean 'return per dollar' of all projects. For the core complete variables, the baseline RMSE using the mean 'return per dollar' was \$0.53 and for the random subset of projects the baseline RMSE ranged between \$0.51 and \$0.56.
